\begin{abstract}

Data science is an interdisciplinary field of study comprising areas such as statistics, computer science and mathematics. In this context, statistical methods are of fundamental importance and, among the possible techniques available for data analysis, regression models play an important role. These models are suitable for problems in which there is an interest in verifying the association between one or more response variables and a set of explanatory variables; this is done by obtaining an equation that explains the relationship between the explanatory variables and the response(s). There are univariate and multivariate models: in univariate models there is only one response variable; in multivariate models there are more than one response. Among the classes of multivariate covariance generalized linear models (McGLMs). It is a flexible class that allows dealing with multiple responses of different types, correlated with each other, in which it is also possible to model the correlation between individuals of the data set. In the context of regression models, a common interest is usually to verify whether the removal of a certain explanatory variable generates a significantly worse model, that is, it is evaluated whether there is enough evidence in the data to state that a certain explanatory variable has no effect on the response. These conjectures are evaluated through so-called hypothesis tests. Three hypothesis tests are common in regression: the likelihood ratio test, the Wald test, and the lagrange multiplier test, also known as the score test. There are also techniques based on hypothesis tests such as analysis of variance (ANOVA) in which the objective is to evaluate the effect of each of the explanatory variables on the response(s); this is done through the comparison via hypothesis tests between models with and without each of the explanatory variables. For the multivariate case, the analysis of variance technique (ANOVA) is extended to the multivariate analysis of variance (MANOVA). However, considering the multivariate covariance generalized linear models, there is no discussion about the construction of these tests for the class. Thus, as it is a flexible class of models with high application power to practical problems, our general goal is the development of hypothesis tests for McGLMs. Our proposal is to adapt the Wald test to perform general hypothesis tests on McGLMs parameters. We aim to implement functions to perform such tests, as well as functions to perform ANOVAs and MANOVAs. The properties and behavior of the proposed tests will be verified based on simulation studies and the potential application of the discussed methodologies will be presented based on their application to real data sets.

\end{abstract}
